---
title: "QualityControl"
author: "Systems biology group- University of Luxembourg"
date: "2023-04-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


set path


```{r}
knitr::opts_knit$set(root.dir = 'C:/Users/maria.pacheco/Documents/GitHub/basicAnalysis/')
```

load libraries
```{r}

library(readr)
library(FactoMineR)
library(factoextra)
#library(FactoInvestigate)
```

Read data and replace NA by zeros
```{r}

fpkm<- read_delim("data/GSE112568_fpkm_table_CRC_C_Williams_Addendum.txt",   delim = "\t", escape_double = FALSE,     trim_ws = TRUE)
fpkm[is.na.data.frame(fpkm)]<-0
```


```

log transform data and transpose data
```{r}
logdata <- t(log2(fpkm[,-c(1,2)]+1))
cond=c('EV', 'EV', 'EV10nME224HR_I',  'EV10nME224HR_I','1uG124hr_I', '1uG124hr_I', 'ERBtransduced','ERBtransduced')
col=cond
pal=c("EV" = "#FF007F", "EV10nME224HR_I" = "#FFAB00", "1uG124hr_I" = "blue", 
      "ERBtransduced" = "#C0CA33") 
```


Do a Principal Component Analysis 

1st and 2nd dimension
```{r}
PC <- PCA(logdata, graph = FALSE)
fviz_pca_ind(PC, col.ind=col,pointshape = 20,pointsize = 2, geom =  c("point", "text"),palette = pal)
```
1st and 3rd dimension
```{r}
PC <- PCA(logdata, graph = FALSE)
#x11()
name=paste("Output/Pca_D1-D3",".png", sep="")
#png(name, width=1000, height=400)
fviz_pca_ind(PC, col.ind=col,pointshape = 20,pointsize = 2, geom =  c("point", "text"),palette = pal,axes=c(1,3))
#dev.off()

```
boxplot
```{r}
x=1:dim(logdata)[1]
x
boxplot(logdata~x,
main = "Data distribution",
names = col,
col = c("gray"),
border = "brown",
horizontal = FALSE,
notch = TRUE
)

```
Density plot
```{r}
color= 1:length(col)
d <- density(logdata[1,])
plot(d,main="density", ylab="Density", xlim=c(0,4))
for (s in 2:length(cond)){
  d <- density(logdata[s,])
  lines(d,col=color[s],xlim=c(0,2))
}
```
Print fpkm
```{r}

name=paste(getwd(),"/Data/FPKM.txt",sep="")
name=gsub("//", "/", name)
name
write.table(fpkm, name)
```
 
